\section{Frequently Asked Questions}
This is a list follows the rubric used by the 18xx Rules Differences
website
(\url{http://www.fwtwr.com/18xx/rules_difference_list/index.htm})

\renewcommand*{\thesubsection}{\arabic{subsection}}

\subsection{First Share Dealing Round}

\subsubsection{How much cash do players start with?}
\begin{tabular}{l|llllll}
Players & 2 & 3 & 4 & 5 & 6 & 7 \\ \hline
Money(円) & 1250 & 840 & 630 & 504 & 420 & 360
\end{tabular}

\subsubsection{Does the price of a private company drop by 5 for no
  sale in the first round?}
Yes, first private only. (\autoref{isr-arima})

\subsubsection{Can you sell company shares in the first round?}
No. (\autoref{sr-sell-restrictions})

\subsubsection{Can you make advance bids?}
Yes, at 5 or more over par and over any other bid. (\autoref{isr-bidding})

\subsection{Subsequent share dealing rounds}

\subsubsection{Is there a specific order to buying and selling on your turn?}
Sell then buy, \emph{or} buy then sell. (\autoref{sr-sell-buy})

\subsubsection{Are you limited to buying one certificate on your turn?}
Yes. (\autoref{sr-buy})

\subsubsection{When can you first sell shares in a company?}
From the second stock round onwards. (\autoref{sr-sell-restrictions})

\subsubsection{Does the bank pool have a per-company share limit?}
50\% (\autoref{sr-sell-restrictions})

\subsubsection{What are the player certificate limits?}
\begin{tabular}{l|llllll}
Players & 2 & 3 & 4 & 5 & 6 & 7\\
\hline
Certificates & 26 & 18 & 15 & 13 & 11 & 10 \\
\end{tabular}

\subsubsection{What are the player certificate limits for shares in one company?}
60\%. Shares in the brown zone do not count towards this. (\autoref{sec:ownership-limit-exceptions})

\subsubsection{Does the stock price drop when stock is sold?}
Yes, 1 row per share. (\autoref{sr-sell-price-drop})

\subsubsection{Does the stock price go up at the end of the share dealing round for a fully-held corporation?}
Yes. (\autoref{sr-sold-out})

\subsubsection{Can you buy a certificate and immediately sell a certificate in the samecompany?}
Yes. (\autoref{sr-sell-buy})

\subsubsection{Can companies buy shares?}
Privates, in ORs, once a 3 train has been sold, and only public
companies. (\autoref{or-private-purchase})

\subsubsection{What ends a share dealing round?}
Each player consecutively not making a purchase or a sale. The
priority then goes to the player after the one who last made a
purchase or a sale. (\autoref{sr-end-of-sr})

\subsection{Company flotation}

\subsubsection{Do you lay the base station token immediately upon floating?}
The token is placed on the home base at the start of the operating
round in which it will first run. (\autoref{or-home-station})

\subsubsection{How many shares must be sold for a company to float?}
Minor companies float when sold in the ISR. Public companies float
when 50\% of shares are sold from the IPO, except for Kinki Nippon
Railways, which floats when a minor company converts into
it. (\autoref{sec:starting-companies})

\subsubsection{Does a company get full capitalization upon floating?}
Yes. (\autoref{floating-initial-capital})

\subsubsection{How is a share company's initial (par) price determined?}
The price is set by the player who purchases the President's
certificate, choosing a value selected from a range of predefined
prices. The purchaser of the Osaka Electric Railway minor company sets
the par price for Kinki. (\autoref{floating-par-price})

\subsection{Operations}

\subsubsection{In what order do companies operate?}
First, minor companies in numeric order, then public companies in
descending share price. If two companies occupy the same space, the
company with its token on top operates first. If two companies have
the same price but in different spaces, the company with its token
furthest to the right operates first. (\autoref{or-operating-order})

\subsubsection{If you sell shares so that their tokens end up in one
  stack, what order are they stacked in?}
Unspecified.

\subsection{Tile Lays}

\subsubsection{Where can you make an initial tile lay?}
As for 1830. (\autoref{or-laying-tiles})

\subsubsection{Can you lay two tiles in a turn?}
Only by using the special property of a private. (\autoref{privates})

\subsubsection{Must a tile replacement extend exiting track?}
Not specified, presumably permissive.

\subsubsection{Do villages upgrade?}
No.

\subsection{Station Markers}

\subsubsection{Cost of station markers}
0 for home bases, 40, 100.

\subsubsection{Can you lay more than one station marker per turn?}
No. (\autoref{or-normal-stations})

\subsubsection{Where can you lay a station marker?}
The newly-laid station marker must be reachable from one of the laying
company's existing station markers by an arbitrarily large
train. (\autoref{or-station-placement-requirements})

\subsubsection{When is a company's first station marker laid?}
When it first operates. (\autoref{or-home-station})

\subsection{Train Runs}

\subsubsection{Can you run into a city completely filled by rival station markers?}
Yes. (\autoref{or-route-definition})

\subsubsection{Can you do a run that passes through a city completely
  filled by rival station markers?}
No, except for Kobe Rapid Transit Railway, and Osaka Subway in
brown. (\autoref{or-route-definition}, \autoref{kobe},
\autoref{osaka-subway})

\subsubsection{Unusual rules about running}
Plus trains (2+2T, 3+3T) can include an additional number of villages
in their run.

\subsubsection{Can one train run to two stations on the same tile?}
Yes. (\autoref{or-route-definition})

\subsubsection{Is double-heading allowed?}
No.

\subsubsection{Rules about villages}
No special rules.

\subsubsection{Must the maximum possible revenue be claimed?}
No. (\autoref{or-route-choice})

\subsection{Payment of Earnings}

\subsubsection{Does stock move right for payment of dividends?}
Yes. (\autoref{or-moving-stock-prices})

\subsubsection{What dividend payments go into the company's treasury?}
Those for shares in the bank pool. (\autoref{or-public-dividends})

\subsubsection{Does stock move left for withheld earnings?}
Yes. (\autoref{or-moving-stock-prices})

\subsubsection{Can a company make a partial payout?}
Minor companies and JR always make a 50\%
payout. (\autoref{or-minor-dividends}, \autoref{JR})

\subsection{Purchasing Trains}

\subsubsection{Can companies buy trains from one another?}
Yes, minimum price 1円. (\autoref{trains-buying-from-companies})

\subsubsection{Must a major share company buy a train if it does not have one?}
If it has a route. (\autoref{train-obligation})

\subsubsection{Can trains be sold back to the bank?}
No.

\subsubsection{When a company is forced to buy a train and connot buy one
  with its own means, what train may it then buy?}
The cheapest train from the open market or the bank. (\autoref{train-force-buy})

\subsubsection{Must a minor company buy a train if it does not have one?}
If it has a route.

\subsubsection{Can trains of the final type be purchased as soon as one
  train of the next-to-last type is purchased?}
Yes. (\autoref{sec:buying-trains})

\subsubsection{Can a company buy more than one train from the bank per OR?}
Yes.

\subsection{Private Companies}

\subsubsection{Are private companies purchaseable between players?}
Yes, on the buyer's turn. (\autoref{sr-buy})

\subsubsection{Are private companies purchaseable by share companies}
Yes. Public companies may purchase privates after a 3-train has been
sold, at from half to twice face value. (\autoref{or-private-purchase})

\subsubsection{Does a private company prevent builds in its home hex(es)
  while it is owned by a player?}
Yes.

\subsubsection{Does using a private company's special property close it?}
Only Osaka Municipal Electric Railway, when Osaka Subway buys its first train.

\subsubsection{When do private companies close?}
When the first 5-train is sold.

\subsubsection{Can you buy and sell private companies in other ways?}
Late private companies may be bought from the bank from SR2 onwards,
but may not be sold to other players or companies.

\subsection{Directorship/Presidency of a Share Company}

\subsubsection{Can you sell the director's certificate into the bank pool?}
No.

\subsubsection{Can you exchange the director's certificate for regular
  shares from another player when you sell shares to the bank pool?}
Yes.

\subsubsection{After a sale of shares forces a change in Director, who
  gets it in case of a tie?}
Next qualifying player on seller's left. (\autoref{shares-change-president})

\subsection{Game Phases}
See \autoref{phase-summary}

\subsection{End of Game}

\subsubsection{Game ends immediately with a bankruptcy?}
Yes. (\autoref{endgame-player-bankruptcy})

\subsubsection{What happens if the bank runs out of money during an
  operating round?}
Game ends at the end of current set of operating
rounds. (\autoref{endgame-bank-break}

\subsubsection{What happens when stock first hits the top end of the market?}
Nothing.

\subsubsection{What happens if the bank runs out of money during a stock
  round?}
Complete the next set of operating rounds. (\autoref{endgame-bank-break})

\subsection{Secrecy}

\subsubsection{Is a player's cash secret, or open for inspection?}
Open. (\autoref{player-cash})

\subsubsection{Is a company's cash secret, or open for inspection?}
Secret. (\autoref{company-charters})

\subsubsection{Is the cash involved in transactions secret, or must it be
  made public?}
Not stated.

\subsubsection{Is the cash in the bank secret, or must it be made public?}
Not stated. Assumed to be public.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "1890rules-en-translation"
%%% End: